Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-23 ApproximateCode-4-23-1557-wu.tex
version Final

\begin{figure}[!ht]
\centering
\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
\includegraphics[height=6cm]{photo/STAR.pdf}\label{fig-star}
}
\hspace{5pt}
\subfigure[\textbf{TIP-Code:} Anti-diagonal parity coding (e.g., $C_{0,6} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{4,4} \oplus C_{5,5}$).]{
\includegraphics[height=6cm]{photo/TIP.pdf}\label{fig-tip}
}\vspace{-3mm}
\caption{Encoding of STAR (Figure \ref{fig-star}) and TIP (Figure \ref{fig-tip}) code ($p = 5$). Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape. STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.}
\vspace{-3mm}
\label{fig-star-tip}
\end{figure}

@@

\begin{table}[ht]\footnotesize
\centering
\caption{
Comparison of storage overhead, fault tolerance and computing overhead among various storage methods for video files}\label{tab-AS-EC-AP}
\begin{tabular}{|p{2cm}<{\centering}|p{1.2cm}<{\centering}|p{1cm}<{\centering}|p{1.1cm}<{\centering}|p{1.1cm}<{\centering}|}
\hline
Schemes & Storage Overhead & Fault Tolerance & Computing Overhead & Layer \\ \hline
Data Compression & low & / & high & \begin{tabular}[c]{@{}c@{}}Application\\Level\end{tabular} \\ \hline
RS-based EC for 3DFTs & high & high & high & \multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}}\\ \cline{1-4} 
XOR-based EC for 3DFTs & high & high & low & \\ \cline{1-4} 
RAID-6 & low & low & low & \\ \cline{1-4} 
RAID-5 & medium & medium & low & \\ \cline{1-4} 
Approximate Storage & very low & very low & low & \\ \cline{1-4} 
Approximate Code & low & high & low & \\ \hline
\end{tabular}
\end{table}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=0.95\linewidth]{photo/Framework-v3.pdf}
\caption{The framework of Approximate Code}
\label{fig-framework}
\end{figure*}

@@

\subsection{Approximate RS-based Codes}\label{appr-rsbased}
The operation of RS($k,m$) is based on the GF, which provides $m$ independent horizontal parities for $k$ data nodes. Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<m)$. RS also supports both two structures. We then introduce the construction of Approximate RS Code and Approximate LRC.

\subsubsection{Approximate RS Code}
We consider the inputted erasure code as RS($4,3$), as shown in Figure \ref{fig-RS-2}. Three horizontal parities are divided into one local and two global parities with the Uneven structure and it generate Approximate RS Code ($4,1,2,3$,Uneven).
As a result, the unimportant data and their corresponding parities constitutes a RS ($4,1$) array, and the important data and their corresponding parities form a RS($4,3$).

@@

\begin{figure}
    \centering
    \subfigure[The generation of APPR.RS Code]{
        \includegraphics[width=0.8\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
    }

    \subfigure[The generation of APPR.LRC]{
        \includegraphics[width=0.8\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
    }
    \caption{The construction and the encoding process of APPR.RS ($4,1,2,3$)}
\end{figure}

\subsection{Approximate XOR-based Codes}\label{APPRXOR}
Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS-based codes. Here we introduce two typical construction of Approximate XOR-based codes, Approximate STAR Code and Approximate TIP-Code.

\begin{figure}[ht]
\centering
\subfigure[Structure selection of APPR.STAR Code]{
    \label{fig-ap-tip-str}
    \includegraphics[width = 0.5\linewidth]{photo/APPR-STAR-STR.pdf}
}

\subfigure[Generation process]{
    \label{fig-ap-tip-GEN}
    \includegraphics[width = \linewidth]{photo/APPR-STAR-GEN.pdf}
}
\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven)}
\label{fig-appr-star}
\end{figure}

\subsubsection{Approximate STAR Code}
Figure \ref{fig-appr-star} shows the construction and the encoding process of APPR.STAR($5,2,1,4$,Uneven).
As introduced in \ref{existEC}, STAR Code \cite{STAR} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
Since STAR is a direct extension of EVENODD\cite{EVENODD}, that is to say, STAR code that removes the anti-diagonal parity is the typical RAID-6 code EVENODD. As shown in Figure \ref{fig-appr-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
According to the construction requirements of STAR, each node is divided into 4 blocks.

Briefly, APPR.STAR($5,2,1,4$,Uneven) can be considered to be important data encoded by the full STAR, while the unimportant data is encoded by a portion of STAR, EVENODD. It is plain to see that important data can tolerate any 3 node failures while unimportant data can tolerate any 2 node failures.

@@

\begin{figure}[ht]
\centering
\subfigure[Structure selection of APPR.TIP-Code]{
    \label{fig-ap-tip-str}
    \includegraphics[width = 0.45\linewidth]{photo/APPR-TIP-STR.pdf}
}
\hspace{2pt}
\subfigure[Generation of local parities]{
    \label{fig-ap-tip-lP}
    \includegraphics[width = 0.3\linewidth]{photo/APPR-TIP-LO.pdf}
}

\subfigure[Generation of global parities]{
    \label{fig-ap-tip-GP}
    \includegraphics[width = 0.8\linewidth]{photo/APPR-TIP-GL-v2.pdf}
}
\caption{The construction and the encoding process of APPR.TIP ($5,1,2,6$,Even). The node 5 and 6 in TIP-Code is defined as the global parity nodes in this case.}
\label{fig-ap-TIP}
\end{figure}

We then introduce the generation of APPR.TIP($5,1,2,6$,Even).

In the code segmentation phase, we split TIP-Code into horizontal, diagonal and anti-diagonal parity. The important data is arranged in Even structure. However, since the parity block of the TIP is distributed over a series of nodes, the code generation process is different from that of the STAR.

We first generate local parity nodes by the horizontal parity for the important and unimportant data in each node. Then, we arrange the important data blocks as the type of Figure \ref{fig-tip-1}.
We use diagonal and anti-diagonal parity to encode the important data and define the last 2 node (Node 5 and 6) as the global parity nodes.

As shown in Figure \ref{fig-ap-TIP}, 30 data nodes form 6 stripes, where important data accounting for 1/6 of each node.
All data nodes generate 6 local parity nodes.
Important data blocks are rearranged to fit the parity form of TIP-Code and generate two global parity nodes.

\subsection{Reconstruction Process and Fault Tolerance}\label{ReconstructionFT}
When $r$ or less nodes fail, all the data can be reconstructed by local parities.
When $r+g$ or less nodes fail, all the important data can be reconstructed by local and global parities.

However, in most cases, the loss of more nodes is also recoverable. We only consider two situations: $r+1$ and $r+g+1$.
The former exceeds the fault tolerance of unimportant data so we calculate the $P_{U}$, while the latter exceeds the fault tolerance of important data and we calculate the $P_{I}$.
As mentioned in Section\ref{code-gen}, $r+g$ is set to 3.

We exhaust all the conditions that may cause data loss and calculate the corresponding probability to calculate $P_{I}$ and $P_{U}$.
Approximate Codes based on different structures also have different fault tolerance and reconstruction cases, so we discuss Even structure and Uneven structure respectively.

\subsubsection{Lost $r+1$ nodes}
Under Even structure, the unimportant data nodes are recoverable as long as the node loss per stripe does not exceed $r$ and the global parity nodes do not need to be considered.
There are $\binom{N}{r+1}$ cases of loss of $r+1$ nodes and $h$ stripes in all. In each stripe, $\binom{k+r}{r+1}$ cases will result in unrecoverable of data.

@@

\subsubsection{Lost $4$ nodes}
The number of all 4-node lost cases is $\binom{N}{4}$.
We calculate the total number of cases in which all important data may be lost based on the different losses of the global parity nodes. The results are as follows:
\begin{align}
    P_{I-Even} = 1 - h*&\frac{\sum_{i=0}^{g} {\binom{k+r}{4-i}*\binom{g}{i}} }{\binom{N}{4}}  (g=1,2)\\
    P_{I-Uneven} &= 1 - \frac{\binom{k+3}{4}}{\binom{N}{4}}
\end{align}

According to the equations above, in Approximate RS ($3,1,2,3$, Even), $80.21\%$ 2-node failure cases are recoverable for unimportant data nodes, and $95.50\%$ 4-node failure is recoverable for important data nodes. In Approximate RS ($3,1,2,3$, Uneven), $P_U=86.81\%$ $P_{I}=98.50\%$.

@@

We analyze the nature of the Approximate Code from the following aspects, and the calculation method of the relevant indicators is given in Table \ref{tab-properties}.
\begin{itemize}
    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating and tiered storage strategies. This property is more pronounced for data with a smaller proportion of important data.
    \item Optimal Update Complexity: When one node is updated, Approximate RS Code only needs to write $r$ local parity nodes and only $g/h$ global parity nodes on average besides the write of data node.
    \item High reliability for important data. The Approximate Code guarantees 3DFTs for important data.
    \item Flexibility. The implementation of the Approximate Code can be based on any erasure codes in 3DFTs.
\end{itemize}

\begin{table}[htb]
\centering
\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, LRC, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP, where $p$ is a prime number.}\label{tab-properties}
\begin{tabular}{|c|c|c|c|}
\hline
EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault\\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Ave Single Write\\ Overhead \end{tabular} \\ \hline
RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
LRC($k,l,r$) & $1+(l+r)/k$ & $r+1$ & $r+2$ \\ \hline
STAR($p$) & $(p+3)/p$ & $3$ & $6-\frac{4}{p}$ \\ \hline
TIP-code($p$) & $\frac{p+1}{P-2}$ & $3$ & 4 \\ \hline
\begin{tabular}[c]{@{}c@{}}APPR.RS\\ ($k,r,g,h$)\end{tabular} & \multirow{3}{*}{$\frac{(k+r)h+g}{kh}$} & $r+g$ & $1+r+\frac{g}{h}$ \\ \cline{1-1} \cline{3-4}
\begin{tabular}[c]{@{}c@{}}APPR.STAR\\ ($k,2,1,h$)\end{tabular} &  & 3 & $2\frac{k-h-1}{kh}+4$ \\ \cline{1-1} \cline{3-4}
\begin{tabular}[c]{@{}c@{}}APPR.TIP\\ ($k,1,2,h$)\end{tabular} &  & 3 & $2+\frac{2}{h}$ \\ \hline
\end{tabular}
\end{table}

\subsection{Implementation}\label{Implementation}
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\linewidth]{photo/implementation-V2.pdf}
\caption{Overview of Approximate Storage Layer}
\label{fig-implementation}
\end{figure}

Compared with the traditional scheme that does not consider the meaning of the upper layer data, the Approximate Code pays attention to the difference of the importance of the data, so an intermediate layer between the upper layer application and the underlying distributed storage system is necessary. We call it the approximate storage layer, which include 3 parts: data identification and allocation, encoding and decoding process of Approximate Code and the video fuzzification and recovery.

\subsubsection{Data Segmentation and Distribution module}
The data segmentation module splits the video file stream into multiple data segments and automatically discriminates the important data. A natural approach is to follow the GOP segmentation. According to the \ref{video storage}, the GOP of the encoded video starts with an I frame, and all the data in that GOP depends on it for decoding, so we define it as important data and divide the GOP into I frames (important part) and other data. (unimportant part).
%The data distribution module distributes important data and unimportant data in different blocks and records the location. This location information is also defined as important data.
This module is also responsible for analyzing the proportion of important data and unimportant data in the data stream to select the most appropriate coding parameter configuration to ensure fault tolerance and high storage efficiency of important data.

\subsubsection{Approximate Code module}
The Approximate Code module is responsible for encoding and decoding important and unimportant data and completely recovering the data within fault tolerance. For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module for approximate recover videos.
%Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each stripe are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.

\subsubsection{Data Fuzzification and Video Recovery}
In the approximate recovery mode, the remaining data and important data are transferred to this module. Using a series of methods described in Section \ref{video storage}, frames that suffer from frame loss will be recovered using the interpolation algorithm; the corrupted frames will be processed into fuzzy images and approximately recovered by superpixel techniques.

>>>>

\begin{figure}[!ht]
\centering
\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
\includegraphics[width=0.42\linewidth]{photo/star-hori.pdf}\label{fig-star-1}
}
\hspace{5pt}
\subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S_1$).]{
\includegraphics[width=0.42\linewidth]{photo/star-diag.pdf}\label{fig-star-2}
}
\vspace{-3mm}
\subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = C_{0,1} \oplus C_{1,2} \oplus C_{2,3} \oplus C_{3,4}$ and $C_{0,7} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{3,3} \oplus S_2$).]{
\includegraphics[width=0.42\linewidth]{photo/star-anti.pdf}\label{fig-star-3}
}
\hspace{5pt}
\subfigure[\textbf{TIP-Code:} Horizontal parity coding (e.g., $C_{0,7} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4} \oplus C_{0,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
}
\vspace{-3mm}
\subfigure[\textbf{TIP-Code:} Diagonal parity coding (e.g., $C_{0,1} = C_{0,0} \oplus C_{5,2} \oplus C_{4,3} \oplus C_{2,5} \oplus C_{1,6}$ ).]{
\includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
}
\hspace{5pt}
\subfigure[\textbf{TIP-Code:} Anti-diagonal parity coding (e.g., $C_{0,6} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{4,4} \oplus C_{5,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-anti.pdf}\label{fig-tip-3}
}\vspace{-3mm}
\caption{\small{Encoding of STAR (Figure \ref{fig-star-1}, \ref{fig-star-2} and \ref{fig-star-3}) and TIP (Figure \ref{fig-tip-1}, \ref{fig-tip-2} and \ref{fig-tip-3}) code ($p = 5$). Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape. STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.}}
\vspace{-3mm}
\label{fig-star-tip}
\end{figure}

@@

\begin{table}[ht]\footnotesize
\centering
\caption{
Comparison of storage overhead, fault tolerance and computing overhead among various storage methods for video files}\label{tab-AS-EC-AP}
\begin{tabular}{|p{1.2cm}<{\centering}|p{2.1cm}<{\centering}|p{1cm}<{\centering}|p{1cm}<{\centering}|p{1cm}<{\centering}|}
\hline
Layer & Schemes & Storage Overhead & Fault Tolerance & Computing Overhead \\ \hline
\begin{tabular}[c]{@{}c@{}}Application\\Level\end{tabular} & Data Compression & low & / & high \\ \hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Device\\Level\end{tabular}} & RS-based EC for 3DFTs & high & high & high \\ \cline{2-5} 
 & XOR-based EC for 3DFTs & high & high & low \\ \cline{2-5} 
 & RAID-6 & low & low & low \\ \cline{2-5} 
 & RAID-5 & medium & medium & low \\ \cline{2-5} 
 & Approximate Storage & very low & very low & low \\ \cline{2-5} 
 & Approximate Code & low & high & low \\ \hline
\end{tabular}
\end{table}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=0.8\linewidth]{photo/Framework-v3.pdf}
\caption{The framework of Approximate Code}
\label{fig-framework}
\end{figure*}

@@

\subsection{Approximate RS-based Codes}\label{appr-rsbased}
RS-based codes are based the calculation of Galois Field (GF), which are designed for arbitrary number of data nodes. Therefore, in the code segmentation step of  Approximate Code framework, we divide the RS-based codes into two parts, $r$ parties and $g$ parities. For structure selection step, the important data can be distributed in both two structures. Here we take RS and LRC codes to show how Approximate Code framework work.

%The operation of RS($k, m$) is based on the GF, which provides $m$ independent horizontal parities for $k$ data nodes. Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<m)$. RS also supports both two structures. We then introduce the construction of Approximate RS Code and Approximate LRC.

\subsubsection{Approximate RS Code}
We consider the inputted erasure code as RS($4,3$), as shown in Figure \ref{fig-RS-2}. Three horizontal parities are divided into one local and two global parities with the Uneven structure, and finally we generate APPR.RS ($4,1,2,3$,Uneven).
As a result, the unimportant data and their corresponding parities constitutes a RS ($4,1$) array, and the important data and their corresponding parities form a RS ($4,3$).

\begin{figure}
    \centering
    \subfigure[The generation of APPR.RS ($4,1,2,3$,Uneven) ]{
        \includegraphics[width=0.8\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
    }

    \subfigure[The generation of APPR.LRC ($4,2,2,3$,Even)]{
        \includegraphics[width=0.8\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
    }
    \caption{Construction of APPR.RS and APPR.LRC codes via Approximate Code framework.}
\end{figure}

@@

We take LRC ($4, 3, 1$) \cite{LRC} as an example (shown in Figure \ref{fig-LRC-2}), which means that three local parities and one global parities are generated initially. Similar to the construction of RS code, two local parities and two global parities are reorganized in the code segmentation step. At last we get the APPR.LRC ($4, 2, 2, 3$, Even).

\subsection{Approximate XOR-based Codes}\label{APPRXOR}
Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding/decoding speed than RS-based codes. Here we introduce two typical construction of Approximate XOR-based codes, Approximate STAR Code and Approximate TIP-Code.

\subsubsection{Approximate STAR Code}

As introduced in Section \ref{existEC}, STAR Code \cite{STAR} is a typical XOR-based erasure code for 3DFTs. STAR is a direct extension of EVENODD\cite{EVENODD} (RAID-6 code) by adding the anti-diagonal parities. Figure \ref{fig-appr-star} shows the construction of APPR.STAR ($5,2,1,4$,Uneven). In this case, the horizontal and diagonal parities are regarded as local parities,  the anti-diagonal parities are defined as global parities in Approximate Code framework.

Briefly, according to the construction of APPR.STAR ($5,2,1,4$, Uneven), the important data are encoded by STAR code while the unimportant data are generated by EVENODD code. It is clear that the important/unimportant data can tolerate triple/double nodes fail, respectively.

\begin{figure}[ht]
\centering
\subfigure[Structure selection.]{
    \label{fig-ap-tip-str}
    \includegraphics[width = 0.5\linewidth]{photo/APPR-STAR-STR.pdf}
}

\subfigure[Generation of APPR.STAR.]{
    \label{fig-ap-tip-GEN}
    \includegraphics[width = \linewidth]{photo/APPR-STAR-GEN.pdf}
}
\caption{Construction of APPR.STAR  ($5,2,1,4$,Uneven) via Approximate Code framework.}
\label{fig-appr-star}
\end{figure}

\begin{figure}[ht]
\centering
\subfigure[Structure selection.]{
    \label{fig-ap-tip-str}
    \includegraphics[width = 0.45\linewidth]{photo/APPR-TIP-STR.pdf}
}
\hspace{2pt}
\subfigure[Local parity generation.]{
    \label{fig-ap-tip-lP}
    \includegraphics[width = 0.3\linewidth]{photo/APPR-TIP-LO.pdf}
}

\subfigure[Global parity generation.]{
    \label{fig-ap-tip-GP}
    \includegraphics[width = 0.8\linewidth]{photo/APPR-TIP-GL-v2.pdf}
}
\caption{Construction of APPR.TIP ($5,1,2,6$,Even) via Approximate Code framework.}
\label{fig-ap-TIP}
\end{figure}

@@

We use the generation of APPR.TIP ($5,1,2,6$,Even) as an example (shown in Figure \ref{fig-ap-TIP}). In the code segmentation phase, we split TIP-Code into two parts, the horizontal parity part, and the diagonal/anti-diagonal parities part. The important data are arranged in Even structure. Since the parities of the TIP-Code are distributed among several nodes, the code generation process is different from APPR.STAR.

We first generate local parity nodes by the horizontal parities for all data. Then, we reorganize the important data to construct new global stripes, where the diagonal and anti-diagonal parities are used to encode the important data. The number of global stripes are based on the ratio of important data ($1/h$). Assume $h=6$, which means that the framework utilizes the important data from six local stripes to generate one global stripe.

\subsection{Reconstruction and Capability of Fault Tolerance}\label{ReconstructionFT}

Existing work \cite{LRC} has demonstrated that when we have $r$ local parities and $g$ global parities, the capability of fault tolerance is at least $r+g$ in typical. Thus the reconstruction (less than $r+g$ nodes fail) of the framework are classified into two cases,

(1) When $r$ or less nodes fail, all data (both important and unimportant data) are reconstructed via local parities.

(2) When $r+g$ or less nodes fail, the important data are reconstructed via both local and global parities.

Under some special cases, for important/unimportant data, exceeding $r+g$/$r+1$ failure nodes is recoverable as well. 
Here we only consider two situations: $r+1$ and $r+g+1$. Assume the recovery probabilities of these two cases are $P_{I}$/$P_{U}$, respectively. Because in this paper we focus on the 3DFTs, $r+g$ is set to 3.

The former exceeds the fault tolerance of unimportant data so we calculate the $P_{U}$, while the latter exceeds the fault tolerance of important data and we calculate the $P_{I}$.
As mentioned in Section\ref{code-gen}, $r+g$ is set to 3.

%We exhaust all the conditions that may cause data loss and calculate the corresponding probability to calculate $P_{I}$ and $P_{U}$.
Approximate Codes based on different structures also have different capabilities of fault tolerance and reconstruction cases, so we discuss Even structure and Uneven structures in the following subsection.

\subsubsection{Lost $r+1$ nodes}
Under Even structure, the unimportant data nodes are recoverable as long as the node losses don't exceed $r$.
There are $\binom{N}{r+1}$ cases of loss of $r+1$ nodes and $h$ stripes in all. In each stripe, $\binom{k+r}{r+1}$ cases result in unrecoverable data.

@@

\subsubsection{Lost $r+g+1$ nodes ($4$ nodes)}
The number of all quad nodes fail cases is $\binom{N}{4}$.
We calculate the total number of cases on losing the important data, which are based on the different losses of the global parity nodes. The results are as follows,
\begin{align}
    P_{I-Even} = 1 - h*&\frac{\sum_{i=0}^{g} {\binom{k+r}{4-i}*\binom{g}{i}} }{\binom{N}{4}}  (g=1,2)\\
    P_{I-Uneven} &= 1 - \frac{\binom{k+3}{4}}{\binom{N}{4}}
\end{align}

According to the above equations, for APPR.RS ($3,1,2,3$, Even), $80.21\%$ double failures cases are recoverable for unimportant data, and $95.50\%$ quad failures is recoverable for important data nodes. For APRR.RS ($3,1,2,3$, Uneven), $P_U=86.81\%$, $P_{I}=98.50\%$.

@@

We analyze the nature of the Approximate Code from the following aspects, and summarize the results shown in Table \ref{tab-properties}.
\begin{itemize}
    \item Low Storage Overhead: Approximate Code reduces storage overhead by approximating and tiered storage strategies for important/unimportant data. 
    \item Low Update Complexity: When one node is updated, APPR. CodeName needs to write $r$ local parity nodes and only $g/h$ global parity nodes, which are less than typical erasure codes.
    \item High reliability for important data. important data can be recovered in all triple nodes failure and most quad nodes failure environment.
    \item High Flexibility. Approximate Code framework can be applied with any erasure codes in 3DFTs, and various parameters can be set.
\end{itemize}

\begin{table}[htb]
\centering
\caption{Comparison of storage overhead, fault tolerance and average single write performance among typical erasure codes and their approximate codes.}\label{tab-properties}
\begin{tabular}{|c|c|c|c|}
\hline
EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault\\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Ave Single Write\\ Overhead \end{tabular} \\ \hline
RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
STAR($p$) & $(p+3)/p$ & $3$ & $6-\frac{4}{p}$ \\ \hline
TIP-code($p$) & $\frac{p+1}{P-2}$ & $3$ & 4 \\ \hline
\begin{tabular}[c]{@{}c@{}}APPR.RS\\ ($k,r,g,h$)\end{tabular} & \multirow{3}{*}{$\frac{(k+r)h+g}{kh}$} & $r+g$ & $1+r+\frac{g}{h}$ \\ \cline{1-1} \cline{3-4}
\begin{tabular}[c]{@{}c@{}}APPR.STAR\\ ($k,2,1,h$)\end{tabular} &  & 3 & $2\frac{k-h-1}{kh}+4$ \\ \cline{1-1} \cline{3-4}
\begin{tabular}[c]{@{}c@{}}APPR.TIP\\ ($k,1,2,h$)\end{tabular} &  & 3 & $2+\frac{2}{h}$ \\ \hline
\end{tabular}
\end{table}

\subsection{Implementation in Storage Systems}\label{Implementation}
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\linewidth]{photo/implementation-V2.pdf}
\caption{Overview of Approximate Storage Layer}
\label{fig-implementation}
\end{figure}

Due to classification of important/unimportant data, the implementation of Approximate Code in storage systems includes three modules (shown in Figure \ref{fig-implementation}), data identification and distribution, approximate code and video recovery.

\subsubsection{Data Identification and Distribution Module}
This module splits the video stream files into multiple data segments, and automatically identifies the important data. A natural approach is to follow the GOP segmentation. According to Section \ref{video storage}, the GOP of the encoded video starts with an I frame, and the remaining data in the GOP depends on it for decoding. Therefore, we define the I frames as the important data, the reminder are unimportant data.
%The data distribution module distributes important data and unimportant data in different blocks and records the location. This location information is also defined as important data.
%This module is also responsible for analyzing the proportion of important data and unimportant data in the data stream to select the most appropriate coding parameter configuration to ensure fault tolerance and high storage efficiency of important data.

\subsubsection{Approximate Code Module}
The Approximate Code module is responsible for encoding/decoding the video data and completely recovering the data. For data that cannot be recovered, the Approximate Code module transmits it to the video recovery module.
%Approximate Code module is also responsible for allocating blocks of data to ensure that blocks of each stripe are distributed to different nodes, while ensuring that global check blocks and data blocks are not on one node.

\subsubsection{Video Recovery Module}
For unrecovered data, the video recovery module using advanced video recovery strategies illustrated in Section \label{video storage}. Generally, the lost frames are recovered using the interpolation algorithms, where the corrupted frames are processed into fuzzy images and approximately recovered by superpixel techniques.
